---
title: "Course Project 1"
author: "Aaron Calderon"
date: "2023-07-30"
output:
  pdf_document: default
  html_document:
    df_print: paged
    code_folding: hide
    toc: yes # INDICE
    toc_float:
      collapse: yes # INDICE MEJORADO 
    number_sections: yes # NUMERACION DE TITULOS
    theme: yeti # TEMA
---

\pagebreak



# Procesamiento

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
setwd("D:/ONLINE/COURSERA/EXPLORATORY DA/COURSERA_EDA/P1")
unzip("exdata_data_household_power_consumption.zip")
data <- read.csv("household_power_consumption.txt",  sep = ";")

data$Date2 <- as.Date(as.character(data$Date), format = "%d/%m/%Y")
data$Datetime <- as.POSIXct(paste(data$Date, data$Time), format = "%d/%m/%Y %H:%M:%S")

data[data$Global_active_power=='?', "Global_active_power"] = NA
data[data$Global_reactive_power=='?', "Global_reactive_power"] = NA
data[data$Voltage=='?', "Voltage"] = NA
data[data$Global_intensity=='?', "Global_intensity"] = NA
data[data$Sub_metering_1=='?', "Sub_metering_1"] = NA
data[data$Sub_metering_2=='?', "Sub_metering_2"] = NA
# data[data$Sub_metering_3=='?', "Sub_metering_3"] = NA

data$Global_active_power <- as.numeric(data$Global_active_power)
data$Global_reactive_power <- as.numeric(data$Global_reactive_power)
data$Voltage <- as.numeric(data$Voltage)
data$Global_intensity <- as.numeric(data$Global_intensity)
data$Sub_metering_1 <- as.numeric(data$Sub_metering_1)
data$Sub_metering_2 <- as.numeric(data$Sub_metering_2)
data$Sub_metering_3 <- as.numeric(data$Sub_metering_3)

dataf <- subset(data, Date2 >= as.Date("2007-02-01") & Date2 <= as.Date("2007-02-02"))
```



# Variables

URL  : Dataset [Electric power consumption](https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2Fhousehold_power_consumption.zip)

* Date: Date in format dd/mm/yyyy

* Time: time in format hh:mm:ss

* Global_active_power: household global minute-averaged active power (in kilowatt)

* Global_reactive_power: household global minute-averaged reactive power (in kilowatt)

* Voltage: minute-averaged voltage (in volt)

* Global_intensity: household global minute-averaged current intensity (in ampere)

* Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered).

* Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.

* Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner.


``` {r, message = FALSE}
head(dataf, 5)
``` 


``` {r, message = FALSE}
as.data.frame(colSums(is.na(dataf)))
``` 



# Plot 1

```{r, message = FALSE}
hist(x = dataf$Global_active_power, 
     breaks = 12, 
     col = "red", 
     main = "Global Active Power",
     xlab = "Global Active Power (kilowatts)"
     )
dev.copy(png, file = "plot1.png", width = 480, height = 480)
dev.off()
```



# Plot 2

```{r, message = FALSE}
# dev.new(width = 480, height = 480, unit = "px")
plot(x = dataf$Datetime, 
     y = dataf$Global_active_power, 
     type = "l",
     main = "",
     ylab = "Global Active Power (kilowatts)",
     xlab = ""
     )
dev.copy(png, file = "plot2.png", width = 480, height = 480)
dev.off()
```



# Plot 3

``` {r, message = FALSE}
# dev.new(width = 480, height = 480, unit = "px")
plot(x = dataf$Datetime, 
     y = dataf$Sub_metering_1, 
     type = "l",
     main = "",
     ylab = "Energy sub metering",
     xlab = "",
     col = "black"
     )
points(x = dataf$Datetime, 
     y = dataf$Sub_metering_2,
     type = "l",
     col = "red"
     )
points(x = dataf$Datetime, 
     y = dataf$Sub_metering_3,
     type = "l",
     col = "blue"
     )
legend(x = "topright",
       cex = 0.7,
       pch = "-", 
       col = c("black", "blue", "red"), 
       legend = c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3")
       )
dev.copy(png, file = "plot3.png", width = 480, height = 480)
dev.off()
``` 



# Plot 4

```{r, message = FALSE}
# dev.new(width = 480, height = 480, unit = "px")
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1), oma = c(0, 0, 2, 0))
with(dataf, {
  plot(Datetime, Global_active_power, ylab = "Global Active Power", type = "l", xlab = "")
  plot(Datetime, Voltage, ylab = "Voltage", type = "l")
  plot(x = dataf$Datetime, 
     y = dataf$Sub_metering_1, 
     type = "l",
     main = "",
     ylab = "Energy sub metering",
     xlab = "",
     col = "black"
     )
  points(x = dataf$Datetime, 
       y = dataf$Sub_metering_2,
       type = "l",
       col = "red"
       )
  points(x = dataf$Datetime, 
       y = dataf$Sub_metering_3,
       type = "l",
       col = "blue"
       )
  legend(x = "topright",
         cex = 0.6,
         pch = "-", 
         col = c("black", "blue", "red"), 
         legend = c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"), bty = "n"
         )
  plot(Datetime, Global_reactive_power, ylab = "Global Reactive Power", type = "l")
})
dev.copy(png, file = "plot4.png", width = 480, height = 480)
dev.off()
```
